ray

### 2022-03-20 outputs/paper/ray.Rmd
transfer text onto rmd

# Older ppl % in upper class
```{r}
old_upper <- raw_data %>% select(c(age, class1))

length(which(old_upper$age > 50 & old_upper$class1 == 6)) / length(which(old_upper$class1 == 6))
```

>>>>

# Older ppl % in upper class
```{r}
old_upper <- raw_data %>% select(c(age, class1, income16, hlthmntl))
length(which(old_upper$age > 50 & old_upper$class1 == 6 & old_upper$income16 < 21)) 
length(which(old_upper$age > 50 & old_upper$class1 == 6 & old_upper$income16 > 21)) / length(which(old_upper$class1 == 6 & old_upper$age > 50))
length(which(old_upper$class1 == 6 & old_upper$age > 50))

length(which(old_upper$age > 50))

length(which(old_upper$class1 == 6))
